On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-09-25 paper.tex
Improved treatment of sigmas

\begin{dfn}
Let $A$ be a ring and $R = A[t, t^{-1}]$ be the ring of Laurent polynomials over $A$.

By definition, a {\it $\sigma$-pair for $\varpi$} is a quadruple $(N(\varpi), N(-\varpi), \sigma(\varpi), \sigma(-\varpi))$ consisting of the following data:
\begin{itemize}
 \item a pair of subgroups $N(\varpi), N(-\varpi) \subseteq \St(\Phi, A[t])$;
 \item a pair of mutually inverse group-theoretic bijections $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$
  fitting into the following commutative diagram:
\begin{equation} \label{eq:sigma-diagram}
\xymatrix{ N(\varpi) \ar@{-->}[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar@{-->}[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
          \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
          \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, R) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, R).} \end{equation}  
\end{itemize}
\end{dfn}

>>>>

\begin{dfn}
By definition, a {\it $\sigma$-pair for $\varpi$} is a pair of mutually inverse group homomorphisms $\sigma(\varpi)\colon N(\varpi) \to N(-\varpi)$, $\sigma(-\varpi)\colon N(-\varpi) \to N(\varpi)$ satisfying
\begin{equation} \label{eq:sigmadef}
\sigma(\pm \varpi)(x_\alpha(\xi)) = x_\alpha(t^{(\pm \varpi, \alpha)}\cdot \xi), 
 \text{ for all } x_\alpha(\xi) \in \mathcal{X}(\pm\varpi).
\end{equation}\end{dfn}
It is clear that any maps $\sigma(\varpi), \sigma(-\varpi)$ satisfying~\eqref{eq:sigmadef} automatically fit into the following commutative diagram:
\begin{equation} \label{eq:sigma-diagram}
\xymatrix{ N(\varpi) \ar[r]^{\sigma(\varpi)}\ar@{^{(}->}[d] & N(-\varpi) \ar@{^{(}->}[d] \ar[r]^{\sigma(-\varpi)} & N(\varpi) \ar@{^{(}->}[d] \\ 
          \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] & \St(\Phi, A[t]) \ar[d] \\
          \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(\varpi, t)} & \St(\Phi, A[t, t^{-1}]) \ar@<-0.0ex>[r]_{\chi(-\varpi, t)} & \St(\Phi, A[t, t^{-1}]).} \end{equation}

\begin{rem} It is clear that the maps $\sigma(\varpi)$, $\sigma(-\varpi)$ are uniquely determined by~\eqref{eq:sigmadef}, so at most one $\sigma$-pair may exist for any given $\varpi$. However, since we have no direct description of the set of relations between the elements of $\mathcal{X}(\varpi)$, we cannot a priori claim that maps $\sigma(\pm\varpi)$ with the property~\eqref{eq:sigmadef} exist.
\end{rem}

\begin{comment}
\begin{itemize}
 \item a pair of subgroups $N(\varpi), N(-\varpi) \subseteq \St(\Phi, A[t])$;
 \item a pair of mutually inverse group-theoretic bijections 
  fitting into the following commutative diagram:
\end{itemize}
\end{comment}
